\bfseries\LARGE Safe Nuclear Power: Instrumentation, Human Oversight, and Infrastructure Transition

### 2025-06-06 Papers/Paper Two/papertwo.tex
add update

\section{Economic Realities and Infrastructure Decline}

@@

\newpage
\printbibliography

\end{document}

This enhanced version keeps your original storytelling and personal reflections intact, while substantially enriching the paper with rigorous research and comprehensive industry analysis.
\section{Conclusion}
Safe nuclear deployment requires integration of robust I\&C logic, disciplined human oversight, and adaptive infrastructure. By applying lessons from both military and civilian history, we can ensure the next generation of nuclear plants are resilient, efficient, and ethically managed.

\newpage
\printbibliography

\end{document}

>>>>

\section{Economic Realities and Infrastructure Decline}
\subsection{United States}
Post-1980s stagnation significantly eroded U.S. nuclear manufacturing capacity, notably in heavy forged reactor components. Universities also witnessed declining nuclear engineering enrollments, exacerbating workforce shortages~\cite{OECD2020}.

\subsection{Global Trends}
Globally, nuclear stagnation prompted industry exits, notably Siemens' post-Fukushima withdrawal~\cite{Reuters2011}, and AREVA's restructuring due to financial difficulties from reactor projects~\cite{WNISR2022}.

\section{Migration from Nuclear to Renewable Energy Sectors}
Economic opportunities led engineering firms like Siemens and General Electric to prioritize renewable energy sectors. Investments in renewables surpassed nuclear by a considerable margin~\cite{WNISR2022,IEA2020}.

\section{Increasing Regulatory Complexity and Costs}
Nuclear plants face escalating regulatory burdens, with annual compliance and licensing costs often totaling tens of millions of dollars per plant, further complicated by stringent post-Fukushima safety mandates~\cite{AAFNuclearCosts}.

\section{Technological Advancements in I\&C and Automation for Safety}
Instrumentation and control (I\&C) advancements significantly enhanced reactor safety and reliability, reducing core damage frequency dramatically. Digital systems improve diagnostics and automate critical responses, bolstered by passive safety measures~\cite{NRCIandC,MIT2020}.

@@

\newpage
\printbibliography
\end{document}
